### 2024-03-22 src/analysis/regression_analysis.Rmd
retrieved missing graphs

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("fixest")
install.packages("tidyr")
install.packages("skimr")
install.packages("infer")
install.packages("modelsummary")
install.packages("broom")
install.packages("purrr")
install.packages("estmatr")
install.packages("pdftools")

library(tidyverse)
library(fixest)
library(tidyr)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
```

@@

```{r plotting results}

#make a plot that suits

@@

>>>>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(tidyr)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
```

@@

```{r plotting results}
#getting the coefficients
list_of_coeficients <- coef(fixed_tth_model)
#getting
list_of_standard_deviations <- se(fixed_tth_model)

# Pivot coefficients longer
list_of_coeficients_long <- list_of_coeficients %>%
  select(!c(sample.var, id)) %>%
  pivot_longer(cols = c(-sample), names_to = "genre", values_to = "coef_value")

# Pivot standard deviations longer
list_of_standard_deviations_long <- list_of_standard_deviations %>%
  select(!c(sample.var, id)) %>%
  pivot_longer(cols = -sample, names_to = "genre", values_to = "std_dev_value")

graph_data <- left_join(list_of_coeficients_long, list_of_standard_deviations_long, by = c("sample", "genre"))

#confidence level, let's say 95%
conf_level <- 0.95
z_value <- qnorm((1 + conf_level) / 2)

graph_data <- graph_data %>%
  drop_na(coef_value) %>%
  mutate(   lower_ci = coef_value - z_value * std_dev_value,
    upper_ci = coef_value + z_value * std_dev_value,
    p_threshold = coef_value / std_dev_value,
    p_significance = ifelse(p_threshold > 1.96, 1, 0))

ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  scale_color_manual(values = c("red", "green")) +
  xlab("Estimates") + ylab("Years") +
  facet_wrap(~ genre)

@@

```{r saving the doc}
#insert pdf knit path
```
